\section{Referencias}

\subsection{Bibliografia}

\begin{itemize}
    \item MARTIN, Robert C. \textbf{Clean Architecture: A Craftsman's Guide to Software Structure and Design}. 1st ed. Boston: Prentice Hall, 2017.
    
    \item FOWLER, Martin. \textbf{Patterns of Enterprise Application Architecture}. Boston: Addison-Wesley Professional, 2002.
    
    \item NIELSEN, Jakob. \textbf{Usability Engineering}. San Francisco: Morgan Kaufmann, 1994.
    
    \item KRUG, Steve. \textbf{Don't Make Me Think: A Common Sense Approach to Web Usability}. 3rd ed. Berkeley: New Riders, 2014.
    
    \item RAMSEY, Dave. \textbf{The Total Money Makeover: A Proven Plan for Financial Fitness}. Nashville: Thomas Nelson, 2013.
    
    \item SETHI, Ramit. \textbf{I Will Teach You to Be Rich}. 2nd ed. New York: Workman Publishing, 2019.
\end{itemize}

\subsection{Documentacao Tecnica}

\begin{itemize}
    \item \textbf{React Documentation}. Available at: \url{https://react.dev/}. Accessed: Jan 2024.
    
    \item \textbf{Node.js Documentation}. Available at: \url{https://nodejs.org/docs/}. Accessed: Jan 2024.
    
    \item \textbf{PostgreSQL Documentation}. Available at: \url{https://www.postgresql.org/docs/}. Accessed: Jan 2024.
    
    \item \textbf{TypeScript Handbook}. Available at: \url{https://www.typescriptlang.org/docs/}. Accessed: Jan 2024.
    
    \item \textbf{React Native Documentation}. Available at: \url{https://reactnative.dev/docs/}. Accessed: Jan 2024.
    
    \item \textbf{Express.js Documentation}. Available at: \url{https://expressjs.com/}. Accessed: Jan 2024.
\end{itemize}

\subsection{Regulamentacoes e Compliance}

\begin{itemize}
    \item \textbf{Lei Geral de Protecao de Dados (LGPD)}. Lei nº 13.709, de 14 de agosto de 2018. Available at: \url{http://www.planalto.gov.br/ccivil_03/_ato2015-2018/2018/lei/l13709.htm}
    
    \item \textbf{Banco Central do Brasil - Open Banking}. Available at: \url{https://www.bcb.gov.br/estabilidadefinanceira/openbanking}
    
    \item \textbf{Web Content Accessibility Guidelines (WCAG) 2.1}. W3C Recommendation. Available at: \url{https://www.w3.org/WAI/WCAG21/}
    
    \item \textbf{Resolucao CMN nº 4.658/2018 - Politica de Seguranca Cibernetica}. Banco Central do Brasil.
\end{itemize}

\subsection{Pesquisas de Mercado}

\begin{itemize}
    \item \textbf{Pesquisa de Endividamento e Inadimplencia do Consumidor (PEIC)}. Confederacao Nacional do Comercio de Bens, Servicos e Turismo, 2023.
    
    \item \textbf{Relatorio de Educacao Financeira no Brasil}. Banco Central do Brasil, 2023.
    
    \item \textbf{Global Fintech Report 2023}. PwC. Available at: \url{https://www.pwc.com/gx/en/industries/financial-services/fintech/}
    
    \item \textbf{State of Personal Finance Apps 2023}. App Annie Intelligence Report.
\end{itemize}

\subsection{Ferramentas e Plataformas}

\begin{itemize}
    \item \textbf{Figma}. Design and prototyping platform. Available at: \url{https://www.figma.com/}
    
    \item \textbf{GitHub}. Code hosting and collaboration platform. Available at: \url{https://github.com/}
    
    \item \textbf{Vercel}. Frontend deployment platform. Available at: \url{https://vercel.com/}
    
    \item \textbf{AWS}. Amazon Web Services cloud platform. Available at: \url{https://aws.amazon.com/}
    
    \item \textbf{Docker}. Containerization platform. Available at: \url{https://www.docker.com/}
    
    \item \textbf{Jira}. Project management and issue tracking. Available at: \url{https://www.atlassian.com/software/jira}
\end{itemize}

\subsection{Estudos de Caso}

\begin{itemize}
    \item \textbf{Mint.com Case Study}: Personal Finance Management Evolution. Harvard Business Review, 2019.
    
    \item \textbf{Nubank: Disrupting Brazilian Banking}. Stanford Graduate School of Business Case Study, 2020.
    
    \item \textbf{YNAB (You Need A Budget): Building a Subscription-Based Personal Finance Platform}. MIT Sloan Case Study, 2021.
    
    \item \textbf{GuiaBolso: Personal Finance in Emerging Markets}. INSEAD Case Study, 2022.
\end{itemize}

\subsection{Artigos e Papers}

\begin{itemize}
    \item LUSARDI, Annamaria; MITCHELL, Olivia S. \textbf{The Economic Importance of Financial Literacy: Theory and Evidence}. Journal of Economic Literature, v. 52, n. 1, p. 5-44, 2014.
    
    \item KLAPPER, Leora; LUSARDI, Annamaria; PANOS, Georgios A. \textbf{Financial literacy and its consequences: Evidence from Russia during the financial crisis}. Journal of Banking \& Finance, v. 37, n. 10, p. 3904-3923, 2013.
    
    \item GOMEZ-MEJIA, Luis R.; BALKIN, David B. \textbf{Effectiveness of Individual and Aggregate Compensation Strategies}. Industrial Relations, v. 28, n. 3, p. 431-445, 1989.
    
    \item BHARGAVA, Saurabh; MANOLI, Dayanand. \textbf{Psychological frictions and the incomplete take-up of social benefits: Evidence from an IRS field experiment}. American Economic Review, v. 105, n. 11, p. 3489-3529, 2015.
\end{itemize}

\subsection{Normas e Padroes}

\begin{itemize}
    \item \textbf{ISO/IEC 27001:2013} - Information Security Management Systems
    
    \item \textbf{ISO/IEC 25010:2011} - Systems and software engineering - Software product Quality Requirements and Evaluation (SQuaRE)
    
    \item \textbf{OWASP Top 10} - The Ten Most Critical Web Application Security Risks
    
    \item \textbf{PCI DSS} - Payment Card Industry Data Security Standard
    
    \item \textbf{RFC 7519} - JSON Web Token (JWT) Standard
\end{itemize}

\subsection{Comunidades e Foruns}

\begin{itemize}
    \item \textbf{Stack Overflow}. Developer community and Q\&A platform. Available at: \url{https://stackoverflow.com/}
    
    \item \textbf{GitHub Discussions}. Open source community discussions. Available at: \url{https://github.com/discussions}
    
    \item \textbf{Reddit - Personal Finance Brazil}. Available at: \url{https://www.reddit.com/r/investimentos/}
    
    \item \textbf{Telegram - Developers Brasil}. Brazilian developers community
    
    \item \textbf{Discord - React Brasil}. React developers community in Brazil
\end{itemize}

\subsection{Cursos e Certificacoes}

\begin{itemize}
    \item \textbf{AWS Certified Solutions Architect}. Amazon Web Services certification program.
    
    \item \textbf{Certified Scrum Master (CSM)}. Scrum Alliance certification.
    
    \item \textbf{Google UX Design Certificate}. Coursera/Google certification program.
    
    \item \textbf{Certified Information Systems Security Professional (CISSP)}. (ISC)² certification.
    
    \item \textbf{React Developer Certification}. Meta/Facebook certification program.
\end{itemize}
